### 2012-07-31 inst/examples/logistic_uniform.Rmd
replace deterministic with tiny growth noise

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="logistic_uniform_c01/", verbose=TRUE or`

@@

``` {r  profit}
price <- 1
c0 <- 0.1
c1 <- 0
profit <- profit_harvest(price=price, c0 = c0, c1=c1) 
````

@@

``` {r }
det <- scenario(0.0, 0.00, 0.00)
````

>>>>

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="logistic_uniform/", verbose=TRUE or`

@@

``` {r  profit}
price <- 1
c0 <- 0
c1 <- 0
profit <- profit_harvest(price=price, c0 = c0, c1=c1) 
````

@@

``` {r }
det <- scenario(0.01, 0.00, 0.00)
````
